\documentclass[9pt, a4paper]{extarticle}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}

% ================== PAGE SETUP ==================
\geometry{
  left=0.5in,
  right=0.5in,
  top=0.28in,
  bottom=0.25in
}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% ================== LIST SPACING ==================
\setlist[itemize]{
  leftmargin=*,
  nosep,
  itemsep=1pt,
  parsep=0pt
}

% ================== HEADING FORMATTING ==================
\titleformat{\section}
  {\Large\bfseries}
  {}
  {0pt}
  {}
\titlespacing*{\section}{0pt}{4pt}{2pt}

\titleformat{\subsection}
  {\large\bfseries}
  {}
  {0pt}
  {}
\titlespacing*{\subsection}{0pt}{3pt}{1.5pt}

\begin{document}
\linespread{0.92}\selectfont
\pagestyle{empty}
\begin{center}
  {\LARGE\textbf{Chenna Reddy Gari Vishnu Vardhan Reddy}} \\[3pt]
  \small
  +91 7671960993 \hspace{0.2em}|\hspace{0.2em}
  vishnuvardhanreddyc57@gmail.com \hspace{0.2em}|\hspace{0.2em}
  \href{https://linkedin.com/in/vishnu57}
       {\underline{LinkedIn}} \hspace{0.2em}|\hspace{0.2em}
  \href{https://github.com/vishnu99617}
       {\underline{GitHub}} \hspace{0.2em}|\hspace{0.2em}
  \href{https://leetcode.com/u/vishnu76719/}
       {\underline{LeetCode}}
\end{center}
\vspace{2pt}

% ================== OBJECTIVE ==================
\section*{Objective}
\vspace{0pt}
\hrule
\vspace{2pt}
Computer Science graduate specializing in B.Tech CSE (Data Science), aspiring to be a Full Stack Java Developer and Data Analyst. Experienced in building scalable microservices using Spring Boot, developing secure REST APIs, and designing Power BI dashboards to translate complex datasets into actionable insights.
\vspace{2pt}

% ================== TECHNICAL SKILLS ==================
\section*{Technical Skills}
\vspace{0pt}
\hrule
\vspace{2pt}
\begin{itemize}
\item \textbf{Programming Languages:} Java (JDK 8/11), Python, SQL
\item \textbf{Frameworks \& Tech:} Spring Boot, Microservices, Spring Security (JWT), RESTful APIs
\item \textbf{Data Analytics \& Visualization:} Power BI, MS Excel (Advanced Pivot Tables, VLOOKUP, Data Analysis)
\item \textbf{Databases \& Storage:} MySQL, PostgreSQL, Relational Database Management Systems (RDBMS)
\item \textbf{Python Libraries \& ML:} NumPy, Pandas, Matplotlib, Seaborn, Scikit-Learn, PyTorch
\item \textbf{Frontend Technologies:} HTML5, CSS3, JavaScript (ES6), Responsive Web Design
\item \textbf{Tools \& Platforms:} Git, GitHub, Postman (API Testing), VS Code, Jupyter Notebook
\item \textbf{Technical Concepts:} Object-Oriented Programming (OOP), Data Structures and Algorithms (DSA), System Design Basics, SDLC (Agile/Scrum), API Integration
\item \textbf{Analytical \& Soft Skills:} Problem Solving, Analytical Thinking, Team Collaboration, Time Management
\end{itemize}
\vspace{2pt}

% ================== EDUCATION ==================
\section*{Education}
\vspace{0pt}
\hrule
\vspace{2pt}
\noindent
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l l l r}
\textbf{G Pulla Reddy Engineering College, Kurnool} 
& \textbf{B.Tech -- CSE (Data Science)} 
& \textbf{2022 -- 2027} 
& \textbf{9.58 CGPA} \\[2pt]
Sri Chaitanya College, Vijayawada 
& Intermediate (MPC) 
& 2020 -- 2022 
& 96.9\% \\[2pt]
ZPH School, Vennapusapalli 
& SSC 
& 2019 -- 2020 
& 96.0\% \\
\end{tabular*}
\vspace{2pt}

% ================== EXPERIENCE ==================
\section*{Experience}
\vspace{0pt}
\hrule
\vspace{2pt}
\subsection*{Devit, Kurnool | JAVA Full Stack Intern \hfill May 2026 -- Present}
\begin{itemize}
\item Engineered 6+ secure RESTful API backend modules for HippocampOS internal management web application.
\item Collaborated in a team of 5+ developers to build scalable Java modules and optimize CI/CD pipelines.
\item Diagnosed and resolved 15+ runtime and API failures using Postman, increasing service reliability.
\end{itemize} 
\subsection*{Infosys Springboard, Remote | Data Visualization Intern \hfill Sep 2025 -- Nov 2025}
\begin{itemize}
\item Developed an interactive Power BI dashboard (Electviz) to visualize and analyze multi-state election datasets.
\item Engineered 10+ custom DAX measures and optimized data models to accelerate report rendering.
\item Synthesized raw election tabular data into interactive charts and maps for data-driven decisions.
\end{itemize}
\vspace{2pt}

% ================== PROJECTS ==================
\section*{Projects}
\vspace{0pt}
\hrule
\vspace{2pt}
\subsection*{AI vs Human Text Detector \href{https://github.com/vishnu99617/ai-vs-human-detector}{\small\normalfont\underline{[Click Here]}} | Spring Boot, Python, MySQL \hfill May 2026}
\begin{itemize}
\item Architected secure microservices backend utilizing Spring Boot, Eureka Server, and API Gateway.
\item Integrated Python NLP service using Machine Learning algorithms to classify text with 94\% accuracy.
\item Designed MySQL database schema to handle 10,000+ history logs and ensured low-latency queries.
\end{itemize}
\subsection*{Job Portal Microservices \href{https://github.com/vishnu99617/job-portal-microservices}{\small\normalfont\underline{[Click Here]}} | Spring Boot, Java, HTML, CSS, JS \hfill June 2026}
\begin{itemize}
\item Engineered a scalable 4-service microservices architecture using Spring Boot to handle job postings.
\item Orchestrated traffic routing and policies through an API Gateway, reducing service coupling.
\item Developed responsive user interface in HTML, CSS, and JS to consume backend REST API endpoints.
\end{itemize}
\subsection*{Electviz -- Election Data Visualization \href{https://github.com/vishnu99617/Infosys_Springboard_Virtual_Internship_6.0_Batch-2_Team-E}{\small\normalfont\underline{[Click Here]}} | Power BI, Excel, DAX \hfill Sep 2025}
\begin{itemize}
\item Designed a Power BI dashboard to analyze multi-region election data, identifying voter trends.
\item Formulated custom DAX queries and designed star-schema models to create interactive reports.
\end{itemize}
\vspace{2pt}

% ================== CERTIFICATIONS ==================
\section*{Certifications}
\vspace{0pt}
\hrule
\vspace{2pt}
\begin{itemize}
  \item \textbf{Java Foundation Certification} -- Infosys Springboard
  \item \textbf{Java \& HTML Fundamentals} -- Spoken Tutorials, IIT Bombay
  \item \textbf{Python Basics for Data Science} -- IBM (edX)
  \item \textbf{Career Essentials in Data Analysis} -- Microsoft \& LinkedIn
  \item \textbf{SQL Certificate} -- HackerRank
\end{itemize}
\end{document}
